---
title: "R SCRIPT"
output: html_document
---

Accompanies Jouffray JB, Wedding L.M., Norstrom A.V., Donovan M.K., Williams G.J., Crowder L.B., Erickson A.L., Friedlander A.M., Graham N.A.J., Gove J.M., Kappel C.V., Kittinger J.N., Lecky J., Oleson K.L.L., Selkoe K.A., White C., Williams I.D., Nystrom M. 2019. Parsing Human and Biophysical Drivers of Coral Reef Regimes. _Proc. R. Soc. B._

**Author:** Jean-Baptiste Jouffray (2019)

**Correspondence:** jean-baptiste.jouffray@su.se

***
***

## Initialisation

***

Need to install [ggBRT](https://github.com/JBjouffray/ggBRT), a set of custom R functions to visualise and interpret the boosted regression tree results. It requires the following R packages: [directlabels](https://cran.r-project.org/web/packages/directlabels/index.html), [dismo](https://cran.r-project.org/web/packages/dismo/index.html), [dplyr](https://cran.r-project.org/web/packages/dplyr/index.html), [ggplot2](https://cran.r-project.org/web/packages/ggplot2/index.html), [ggthemes](https://cran.r-project.org/web/packages/ggthemes/index.html), [gridExtra](https://cran.r-project.org/web/packages/gridExtra/index.html), [plotly](https://cran.r-project.org/web/packages/plotly/index.html), [plyr](https://cran.r-project.org/web/packages/plyr/index.html) and [reshape2](https://cran.r-project.org/web/packages/reshape2/index.html).

```{r setup, eval=FALSE}
# Install ggBRT 
install.packages("devtools") # if package "devtools" not already installed
devtools::install_github("JBjouffray/ggBRT")
library(ggBRT)

# Import data
dat<-read.delim("Hawaii_RegimesPredictors.txt",h=T,dec=",")
PredictorsCat<-read.delim("Hawaii_PredictorsCategories.txt",h=T,dec=",")
```

## Summary of the regimes
***
The study builds on data from 620 sites classified into four reef regimes using model-based clustering of ten fish and benthic functional groups.

```{r, eval=FALSE}
# Summary statistics of the regimes' components
ddply(melt(dat[,c(5:14,35)], id.vars=c("Regime")), c("Regime", "variable"), summarise,
         mean = round(mean(value),1),
         sem = round(2*(sd(value)/sqrt(length(value))),1))
```

## Collinearity
***

We use pairwise relationship correlation coefficients and variance inflation factor estimates to assess collinearity among predictors. The data presented here (i.e., Hawaii_RegimesPredictors.txt) is already a subset resulting from multiple collinearity analyses.

```{r, eval=FALSE}
# Select the set of 20 predictors
pred<-c(15:34)

# Assess collinearity with Pearson correlation coefficient
library(corrplot)
coeff<-cor(dat[,pred], method="pearson",use="pairwise.complete.obs")
coeff[which(abs(coeff[])>0.6)] # no correlation > 0.6

# Correlation plot
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(coeff,method="number", col=col(200),tl.cex=0.8,number.cex = 0.7,
         tl.col="black", tl.srt=45)

# Assess collinearity with Variable Inflation Factor
source("vif_func.R") # available at https://gist.github.com/fawda123/4717702#file-vif_fun-r
vif_func(in_frame=dat[,pred],thresh=4,trace=T) # all variables have VIF < 4, max VIF 3.28 
```

## Boosted regression trees (BRT)
***

We use BRT to examine the occurrence of each regime in relation to anthropogenic and biophysical predictors. Trees are built with set default parameters to make model outputs comparable among regimes: a tree complexity of 5, a learning rate of 0.001 and a bag fraction of 0.75. Variation of these parameters provided negligible improvements in predictive performance. Note that the results and model's performance can vary slightly because of stochasticity.

```{r, eval=FALSE}
set.seed(1) 
brt1 <- gbm.step(data=dat, gbm.x = pred, gbm.y = which(names(dat) == 'Regime1'),
                 family = "bernoulli", tree.complexity = 5,
                 learning.rate = 0.001, bag.fraction = 0.75)
brt2 <- gbm.step(data=dat, gbm.x = pred, gbm.y = which(names(dat) == 'Regime2'),
                 family = "bernoulli", tree.complexity = 5,
                 learning.rate = 0.001, bag.fraction = 0.75)
brt3 <- gbm.step(data=dat, gbm.x = pred, gbm.y = which(names(dat) == 'Regime3'),
                 family = "bernoulli", tree.complexity = 5,
                 learning.rate = 0.001, bag.fraction = 0.75)
brt5 <- gbm.step(data=dat, gbm.x = pred, gbm.y = which(names(dat) == 'Regime5'),
                 family = "bernoulli", tree.complexity = 5,
                 learning.rate = 0.001, bag.fraction = 0.75)

# Extract the performance of the models
Perf<-ggPerformance(Regime1=brt1,Regime2=brt2,Regime3=brt3,Regime5=brt5)
round(Perf,2)
```

## Relative influence of predictors
***

To assess the relative contribution of anthropogenic versus biophysical predictors for each regime, we considered only the variables with a relative influence above that expected by chance (100/number of variables, i.e. 5%) and rescaled their influence to 100%.

```{r, eval=FALSE}
# Plot relative influence of predictors for each regime
ggInfluence(brt1,col.bar = "grey70")
ggInfluence(brt2,col.bar = "grey70")
ggInfluence(brt3,col.bar = "grey70")
ggInfluence(brt5,col.bar = "grey70")

# Plot relative influence of predictors for all regimes at once
ggMultiInfluence(Regime1=brt1,Regime2=brt2,Regime3=brt3,Regime5=brt5)

# Extract relative influence of biophysical versus anthropogenic
ggCatInfluence(brt1,brt2,brt3,brt5,category = "Category",data=PredictorsCat)

# Extract relative influence of biophysical versus anthropogenic by considering only the variables with a relative influence above that expected by chance
ggCatInfluence(brt1,brt2,brt3,brt5,category = "Category",data=PredictorsCat,signif=T)
```

## Partial dependency plots
***

Partial dependency plots with 95% confidence intervals obtained from 1000 bootstrap replicates are used to visualize the relationships between the most influential predictor variables and the response (regime), while keeping all other predictors at their mean. 

```{r, eval=FALSE}
# Boostrap the BRTs 1000 times for each regime to build confidence intervals
brt1.prerun<- plot.gbm.4list(brt1)
brt1.boot <- gbm.bootstrap.functions(brt1, list.predictors=brt1.prerun, n.reps=1000)

brt2.prerun<- plot.gbm.4list(brt2)
brt2.boot <- gbm.bootstrap.functions(brt2, list.predictors=brt2.prerun, n.reps=1000)

brt3.prerun<- plot.gbm.4list(brt3)
brt3.boot <- gbm.bootstrap.functions(brt3, list.predictors=brt3.prerun, n.reps=1000)

brt5.prerun<- plot.gbm.4list(brt5)
brt5.boot <- gbm.bootstrap.functions(brt5, list.predictors=brt5.prerun, n.reps=1000)

# Save the models outcome
save(brt1,brt2,brt3,brt5,
     brt1.boot,brt2.boot,brt3.boot,brt5.boot,
     brt1.prerun,brt2.prerun,brt3.prerun,brt5.prerun, file = "BRT_RegimesPredictors.Rdata") 
load(file = "BRT_RegimesPredictors.Rdata")

# Draw partial dependency plots for the five most influential predictors
ggPD_boot(brt1,n.plots = 5, nrow=1,list.4.preds=brt1.prerun, col.line="#CF4D46",
          booted.preds=brt1.boot$function.preds, cex.line=1, col.ci="#CF4D46",
          alpha.dot=0.2,type.ci = "ribbon",alpha.ci=0.1,rug = T,y.label = "")

ggPD_boot(brt2,n.plots = 6, nrow=1,list.4.preds=brt2.prerun, col.line="#5576AF",
          booted.preds=brt2.boot$function.preds, cex.line=1, col.ci="#5576AF",
          alpha.dot=0.2,type.ci = "ribbon",alpha.ci=0.1,rug = T,y.label = "")

ggPD_boot(brt3,n.plots = 5, nrow=1,list.4.preds=brt3.prerun, col.line="#DDAB34",
          booted.preds=brt3.boot$function.preds, cex.line=1, col.ci="#DDAB34",
          alpha.dot=0.2,type.ci = "ribbon",alpha.ci=0.1,rug = T,y.label = "")

ggPD_boot(brt5,n.plots = 5, nrow=1,list.4.preds=brt5.prerun, col.line="#79A45A",
          booted.preds=brt5.boot$function.preds, cex.line=1, col.ci="#79A45A",
          alpha.dot=0.2,type.ci = "ribbon",alpha.ci=0.1,rug = T,y.label = "")
```

## Interactions between predictors
***

We quantify relative interaction strength between predictor by measuring residual variation between pairwise model predictions with and without interactions.

```{r,eval=FALSE}
# Regime 1 #
ggInteract_list(brt1)

# Randomization of the response to test significance of the three strongest interactions. Note, the parameters need to be the same as your BRT model
Interact_boot_brt1<-ggInteract_boot(c('Complexity','Fishing_NonComm_Boat_Total'),
                                    c('Complexity','Fishing_Comm_Total'),
                                    c('Depth','Complexity'),
                                    nboots = 100,data=dat, predictors = pred, response=which(names(dat) == 'Regime1'),
                                    family = "bernoulli", tc = 5, lr = 0.001, bf= 0.75,global.env=F)

# Significance histogram (99% CI => p-value=0.01)
ggInteract_boot_hist(data = Interact_boot_brt1,column = 2,obs = 27.97,
                     cis=c(0.005, 0.995),bindwidth = 0.1)
ggInteract_boot_hist(data = Interact_boot_brt1,column = 3,obs = 27.76,
                     cis=c(0.005, 0.995),bindwidth = 0.1)

# 2D interaction plots of the two strongest interactions
ggInteract_2D(gbm.object = brt1,x="Complexity",y="Fishing_NonComm_Boat_Total",col.gradient = c("white","#CF4D46"),
              show.dot = T,col.dot = "grey20",alpha.dot = 0.5,cex.dot = 0.2,
              label.contour = T,col.contour = "#92271F",show.axis = T,legend = T)

ggInteract_2D(gbm.object = brt1,x="Complexity",y="Fishing_Comm_Total",col.gradient = c("white","#CF4D46"),
              show.dot = T,col.dot = "grey20",alpha.dot = 0.5,cex.dot = 0.2,
              label.contour = T,col.contour = "#92271F",show.axis = T,legend = T)

# Regime2 #
ggInteract_list(brt2)

# Randomization of the response to test significance of interaction
Interact_boot_brt2<-ggInteract_boot(c('WAV_CLIM_M','SST_STD'),
                                    c('Depth','WAV_CLIM_M'),
                                    c('SST_STD','SST_CLIM_M'),
                                    nboots = 100,data=dat, predictors = pred, response=which(names(dat) == 'Regime2'),
                                    family = "bernoulli", tc = 5, lr = 0.001, bf= 0.75,global.env=F)

# Significance histogram (99% CI => p-value=0.01)
ggInteract_boot_hist(data = Interact_boot_brt2,column = 2,obs = 64.82,
                     cis=c(0.005, 0.995),bindwidth = 0.1)
ggInteract_boot_hist(data = Interact_boot_brt2,column = 3,obs = 18.51,
                     cis=c(0.005, 0.995),bindwidth = 0.1)

# 2D interaction plots of the two strongest interactions
ggInteract_2D(gbm.object = brt2,x="WAV_CLIM_M",y="SST_STD",col.gradient = c("white","#5576AF"),
              show.dot = T,col.dot = "grey20",alpha.dot = 0.5,cex.dot = 0.2,
              label.contour = T,col.contour = "#254376",show.axis = T,legend = T)

ggInteract_2D(gbm.object = brt2,x="Depth",y="WAV_CLIM_M",col.gradient = c("white","#5576AF"),
              show.dot = T,col.dot = "grey20",alpha.dot = 0.5,cex.dot = 0.2,
              label.contour = T,col.contour = "#254376",show.axis = T,legend = T)


# Regime3 #
ggInteract_list(brt3)

# Randomization of the response to test significance of interaction
Interact_boot_brt3<-ggInteract_boot(c('PAR_STD','SST_CLIM_M'),
                                    c('Complexity','PAR_CLIM_M'),
                                    c('Complexity','WAV_CLIM_M'),
                                    nboots = 100,data=dat, predictors = pred, response=which(names(dat) == 'Regime3'),
                                    family = "bernoulli", tc = 5, lr = 0.001, bf= 0.75,global.env=F)

# Significance histogram (99% CI => p-value=0.01)
ggInteract_boot_hist(data = Interact_boot_brt3,column = 2,obs = 11.91,
                     cis=c(0.005, 0.995),bindwidth = 0.1)
ggInteract_boot_hist(data = Interact_boot_brt3,column = 3,obs = 11.47,
                     cis=c(0.005, 0.995),bindwidth = 0.1)

# 2D interaction plots of the two strongest interactions
ggInteract_2D(gbm.object = brt3,x="PAR_STD",y="SST_CLIM_M",col.gradient = c("white","#DDAB34"),
              show.dot = T,col.dot = "grey20",alpha.dot = 0.5,cex.dot = 0.2,
              label.contour = T,col.contour = "#AF7E0B",show.axis = T,legend = T)

ggInteract_2D(gbm.object = brt3,x="Complexity",y="PAR_CLIM_M",col.gradient = c("white","#DDAB34"),
              show.dot = T,col.dot = "grey20",alpha.dot = 0.5,cex.dot = 0.2,
              label.contour = T,col.contour = "#AF7E0B",show.axis = T,legend = T)


# Regime5 #
ggInteract_list(brt5)

# Randomization of the response to test significance of interaction
Interact_boot_brt5<-ggInteract_boot(c('PAR_STD','Invasive_Algae'),
                                    c('Depth','Fishing_NonComm_Boat_Total'),
                                    c('SST_STD','SST_CLIM_M'),
                                    nboots = 100,data=dat, predictors = pred, response=which(names(dat) == 'Regime5'),
                                    family = "bernoulli", tc = 5, lr = 0.001, bf= 0.75,global.env=F)

# Significance histogram
ggInteract_boot_hist(data = Interact_boot_brt5,column = 2,obs = 25.35,
                     cis=c(0.005, 0.995), bindwidth = 0.1)
ggInteract_boot_hist(data = Interact_boot_brt5,column = 3,obs = 15.55,
                     cis=c(0.005, 0.995), bindwidth = 0.1)

# 2D interaction plots of the two strongest interactions
ggInteract_2D(gbm.object = brt5,x="PAR_STD",y="Invasive_Algae",col.gradient = c("white","#79A45A"),
              show.dot = T,col.dot = "grey20",alpha.dot = 0.5,cex.dot = 0.2,
              label.contour = T,col.contour = "#3E6C20",show.axis = T,legend = T)

ggInteract_2D(gbm.object = brt5,x="Depth",y="Fishing_NonComm_Boat_Total",col.gradient = c("white","#79A45A"),
              show.dot = T,col.dot = "grey20",alpha.dot = 0.5,cex.dot = 0.2,
              label.contour = T,col.contour = "#3E6C20",show.axis = T,legend = T)
```

## Scale analysis 
***

To control for the influence of different predictor's grain sizes on the outcome of the model, we extracted all predictor raster datasets at multiple standardized grain sizes (500m, 1000m, 1500m, 2500m, 4000m), before re-running the BRT on regimes aggregated following a two-thirds majority within each cell resolution.

```{r, eval=FALSE}
# Import data (one file for each scale: 500, 1000, 1500, 2500 and 4000). For brevity, 
# of the script, overwrite the names and run all lines again...and so on.
datScale<-read.delim("scale_500.txt",h=T,dec=",")

# Retain only the sites for which a 2/3rd majority could be calculated
datScale<-subset(datScale,datScale$Majority=="two_thirds")

# Select set of predictors
predScale<-c(3,4,15:19,22,26,31:38,40:42)

# Assess collinearity with Pearson
cor<-cor(datScale[,predScale], method="pearson",use="pairwise.complete.obs")
w<-which(abs(cor[])>0.6)
cor[w]

# Assess collinearity with Variable Inflation Factor
source("vif_func.R")
vif_func(in_frame=dat[,predScale],thresh=4.1,trace=T)

# Run BRT for each regime with set parameters: tc=5; lr=0.001; bf=0.75.
# Note that the results will always vary slightly because of stochasticity
set.seed(1)
brt1 <- gbm.step(data=datScale, gbm.x = predScale, gbm.y = which(names(datScale) == 'Regime1'),
                 family = "bernoulli", tree.complexity = 5,
                 learning.rate = 0.001, bag.fraction = 0.75)
brt2 <- gbm.step(data=datScale, gbm.x = predScale, gbm.y = which(names(datScale) == 'Regime2'),
                 family = "bernoulli", tree.complexity = 5,
                 learning.rate = 0.001, bag.fraction = 0.75)
brt3 <- gbm.step(data=datScale, gbm.x = predScale, gbm.y = which(names(datScale) == 'Regime3'),
                 family = "bernoulli", tree.complexity = 5,
                 learning.rate = 0.001, bag.fraction = 0.75)
brt5 <- gbm.step(data=datScale, gbm.x = predScale, gbm.y = which(names(datScale) == 'Regime5'),
                 family = "bernoulli", tree.complexity = 5,
                 learning.rate = 0.001, bag.fraction = 0.75)

brt1_500<-brt1
brt2_500<-brt2
brt3_500<-brt3
brt5_500<-brt5

# Go back to beginning, import data at a new scale (1000m) and repeat the BRTs
brt1_1000<-brt1
brt2_1000<-brt2
brt3_1000<-brt3
brt5_1000<-brt5

# Go back to beginning, import data at a new scale (1500m) and repeat the BRTs
brt1_1500<-brt1
brt2_1500<-brt2
brt3_1500<-brt3
brt5_1500<-brt5

# Go back to beginning, import data at a new scale (2500m) and repeat the BRTs
brt1_2500<-brt1
brt2_2500<-brt2
brt3_2500<-brt3
brt5_2500<-brt5

# Go back to beginning, import data at a new scale (4000m) and repeat the BRTs
brt1_4000<-brt1
brt2_4000<-brt2
brt3_4000<-brt3
brt5_4000<-brt5

# Boostrap the BRTs 1000 times for each regime at each scale to build confidence intervals
#500m
brt1_500.prerun<- plot.gbm.4list(brt1_500)
brt1_500.boot <- gbm.bootstrap.functions(brt1_500, list.predictors=brt1_500.prerun, n.reps=1000)

brt2_500.prerun<- plot.gbm.4list(brt2_500)
brt2_500.boot <- gbm.bootstrap.functions(brt2_500, list.predictors=brt2_500.prerun, n.reps=1000)

brt3_500.prerun<- plot.gbm.4list(brt3_500)
brt3_500.boot <- gbm.bootstrap.functions(brt3_500, list.predictors=brt3_500.prerun, n.reps=1000)

brt5_500.prerun<- plot.gbm.4list(brt5_500)
brt5_500.boot <- gbm.bootstrap.functions(brt5_500, list.predictors=brt5_500.prerun, n.reps=1000)

#1000m
brt1_1000.prerun<- plot.gbm.4list(brt1_1000)
brt1_1000.boot <- gbm.bootstrap.functions(brt1_1000, list.predictors=brt1_1000.prerun, n.reps=1000)

brt2_1000.prerun<- plot.gbm.4list(brt2_1000)
brt2_1000.boot <- gbm.bootstrap.functions(brt2_1000, list.predictors=brt2_1000.prerun, n.reps=1000)

brt3_1000.prerun<- plot.gbm.4list(brt3_1000)
brt3_1000.boot <- gbm.bootstrap.functions(brt3_1000, list.predictors=brt3_1000.prerun, n.reps=1000)

brt5_1000.prerun<- plot.gbm.4list(brt5_1000)
brt5_1000.boot <- gbm.bootstrap.functions(brt5_1000, list.predictors=brt5_1000.prerun, n.reps=1000)

#1500m
brt1_1500.prerun<- plot.gbm.4list(brt1_1500)
brt1_1500.boot <- gbm.bootstrap.functions(brt1_1500, list.predictors=brt1_1500.prerun, n.reps=1000)

brt2_1500.prerun<- plot.gbm.4list(brt2_1500)
brt2_1500.boot <- gbm.bootstrap.functions(brt2_1500, list.predictors=brt2_1500.prerun, n.reps=1000)

brt3_1500.prerun<- plot.gbm.4list(brt3_1500)
brt3_1500.boot <- gbm.bootstrap.functions(brt3_1500, list.predictors=brt3_1500.prerun, n.reps=1000)

brt5_1500.prerun<- plot.gbm.4list(brt5_1500)
brt5_1500.boot <- gbm.bootstrap.functions(brt5_1500, list.predictors=brt5_1500.prerun, n.reps=1000)

#2500m
brt1_2500.prerun<- plot.gbm.4list(brt1_2500)
brt1_2500.boot <- gbm.bootstrap.functions(brt1_2500, list.predictors=brt1_2500.prerun, n.reps=1000)

brt2_2500.prerun<- plot.gbm.4list(brt2_2500)
brt2_2500.boot <- gbm.bootstrap.functions(brt2_2500, list.predictors=brt2_2500.prerun, n.reps=1000)

brt3_2500.prerun<- plot.gbm.4list(brt3_2500)
brt3_2500.boot <- gbm.bootstrap.functions(brt3_2500, list.predictors=brt3_2500.prerun, n.reps=1000)

brt5_2500.prerun<- plot.gbm.4list(brt5_2500)
brt5_2500.boot <- gbm.bootstrap.functions(brt5_2500, list.predictors=brt5_2500.prerun, n.reps=1000)

#4000m
brt1_4000.prerun<- plot.gbm.4list(brt1_4000)
brt1_4000.boot <- gbm.bootstrap.functions(brt1_4000, list.predictors=brt1_4000.prerun, n.reps=1000)

brt2_4000.prerun<- plot.gbm.4list(brt2_4000)
brt2_4000.boot <- gbm.bootstrap.functions(brt2_4000, list.predictors=brt2_4000.prerun, n.reps=1000)

brt3_4000.prerun<- plot.gbm.4list(brt3_4000)
brt3_4000.boot <- gbm.bootstrap.functions(brt3_4000, list.predictors=brt3_4000.prerun, n.reps=1000)

brt5_4000.prerun<- plot.gbm.4list(brt5_4000)
brt5_4000.boot <- gbm.bootstrap.functions(brt5_4000, list.predictors=brt5_4000.prerun, n.reps=1000)


# Save the models outcome
save(brt1_500,brt2_500,brt3_500,brt5_500,
     brt1_1000,brt2_1000,brt3_1000,brt5_1000,
     brt1_1500,brt2_1500,brt3_1500,brt5_1500,
     brt1_2500,brt2_2500,brt3_2500,brt5_2500,
     brt1_4000,brt2_4000,brt3_4000,brt5_4000,
     brt1_500.boot,brt2_500.boot,brt3_500.boot,brt5_500.boot,
     brt1_1000.boot,brt2_1000.boot,brt3_1000.boot,brt5_1000.boot,
     brt1_1500.boot,brt2_1500.boot,brt3_1500.boot,brt5_1500.boot,
     brt1_2500.boot,brt2_2500.boot,brt3_2500.boot,brt5_2500.boot,
     brt1_4000.boot,brt2_4000.boot,brt3_4000.boot,brt5_4000.boot,
     file = "SCALE_Hawaii_RegimesPredictors.Rdata")

load(file = "SCALE_Hawaii_RegimesPredictors.Rdata")

# Extract the performance of the models
ggPerformance(brt1_500=brt1_500,brt2_500=brt2_500,brt3_500=brt3_500,brt5_500=brt5_500,
                    brt1_1000=brt1_1000,brt2_1000=brt2_1000,brt3_1000=brt3_1000,brt5_1000=brt5_1000,
                    brt1_1500=brt1_1500,brt2_1500=brt2_1500,brt3_1500=brt3_1500,brt5_1500=brt5_1500,
                    brt1_2500=brt1_2500,brt2_2500=brt2_2500,brt3_2500=brt3_2500,brt5_2500=brt5_2500,
                    brt1_4000=brt1_4000,brt2_4000=brt2_4000,brt3_4000=brt3_4000,brt5_4000=brt5_4000)

# Plot relative influence of predictors (repeat for each BRT)
ggInfluence(brt1_500)

# Draw partial dependency plots of five most influential predictors (repeat for each BRT)
ggPD_boot(brt1_500,n.plots = 5, nrow=1,list.4.preds=brt1_500.prerun, col.line="#CF4D46",
          booted.preds=brt1_500.boot$function.preds, cex.line=1, col.ci="#CF4D46",
          alpha.dot=0.2,type.ci = "ribbon",alpha.ci=0.1,rug = T,y.label = "")

# Retrieve anthropogenic versus biophysical relative influence 
ggCatInfluence(brt1_500=brt1_500,brt2_500=brt2_500,brt3_500=brt3_500,brt5_500=brt5_500,
                  brt1_1000=brt1_1000,brt2_1000=brt2_1000,brt3_1000=brt3_1000,brt5_1000=brt5_1000,
                  brt1_1500=brt1_1500,brt2_1500=brt2_1500,brt3_1500=brt3_1500,brt5_1500=brt5_1500,
                  brt1_2500=brt1_2500,brt2_2500=brt2_2500,brt3_2500=brt3_2500,brt5_2500=brt5_2500,
                  brt1_4000=brt1_4000,brt2_4000=brt2_4000,brt3_4000=brt3_4000,brt5_4000=brt5_4000,
                  category = "Category",data=PredictorsCat)

ggCatInfluence_signif(brt1_500=brt1_500,brt2_500=brt2_500,brt3_500=brt3_500,brt5_500=brt5_500,
                       brt1_1000=brt1_1000,brt2_1000=brt2_1000,brt3_1000=brt3_1000,brt5_1000=brt5_1000,
                       brt1_1500=brt1_1500,brt2_1500=brt2_1500,brt3_1500=brt3_1500,brt5_1500=brt5_1500,
                       brt1_2500=brt1_2500,brt2_2500=brt2_2500,brt3_2500=brt3_2500,brt5_2500=brt5_2500,
                       brt1_4000=brt1_4000,brt2_4000=brt2_4000,brt3_4000=brt3_4000,brt5_4000=brt5_4000,
                       category = "Category",data=PredictorsCat)
```

## Plots of model performance and relative influence across scales
***

```{r, eval=FALSE}
# Cross-validated deviance explained
datScalePerf<-read.table("ModelPerf_Across_Scales.txt",h=T, dec=",")
datScalePerf<-subset(datScalePerf,datScalePerf$Parameter=="cvPer.Expl")
datScalePerf$Scale<-as.factor(datScalePerf$Scale)

ggplot(datScalePerf)+
  geom_boxplot(aes(x=Scale, y=Value),coef=2,fill = "grey90", colour = "grey30")+
  geom_point(aes(x=Scale,y=Value,colour=Regime,shape=Regime),size=3,alpha=0.8)+
  scale_colour_manual(name = '',values=c("#CF4D46", "#5576AF", "#DDAB34","#79A45A"))+
  scale_shape_manual(name = '',values=c(4,15,17,16))+
  labs(x="Grain size (m)", y="Cross-validated deviance explained (%) ")+
  ylim(0,100)+
  theme_bw()+
  theme(panel.grid=element_blank(),
        legend.position = "right",
        axis.text.x  = element_text(size=14),
        axis.text.y  = element_text(size=14))


# Cross-validated area under the receiver operating character (AUC)
datScalePerf<-read.table("ModelPerf_Across_Scales.txt",h=T, dec=",")
datScalePerf<-subset(datScalePerf,datScalePerf$Parameter=="cvAUC")
datScalePerf$Scale<-as.factor(datScalePerff$Scale)

ggplot(datScalePerf)+
  geom_boxplot(aes(x=Scale, y=Value),coef=2,fill = "grey90", colour = "grey30")+
  geom_point(aes(x=Scale,y=Value,colour=Regime,shape=Regime),size=3,alpha=0.8)+
  scale_colour_manual(name = '',values=c("#CF4D46", "#5576AF", "#DDAB34","#79A45A"))+
  scale_shape_manual(name = '',values=c(4,15,17,16))+
  labs(x="Grain size (m)", y="Cross-validated AUC")+
  ylim(0.5,1)+
  theme_bw()+
  theme(panel.grid=element_blank(),
        legend.position = "right",
        axis.text.x  = element_text(size=14),
        axis.text.y  = element_text(size=14))


# Relative influence of anthropogenic predictors
datScaleRel<-read.table("RelInfluence_Across_Scales.txt",h=T, dec=",")
datScaleRel<-subset(datScaleRel,datScaleRel$Category=="Anthropogenic")
datScaleRel$Scale<-as.factor(datScaleRel$Scale)

ggplot(datScaleRel)+
  geom_boxplot(aes(x=Scale, y=Sig_Influence),coef=2,fill = "grey90", colour = "grey30")+
  geom_point(aes(x=Scale,y=Sig_Influence,colour=Regime,shape=Regime),size=3,alpha=0.8)+
  scale_colour_manual(name = '',values=c("#CF4D46", "#5576AF", "#DDAB34","#79A45A"))+
  scale_shape_manual(name = '',values=c(4,15,17,16))+
  labs(x="Grain size (m)", y="Anthropogenic relative influence (%) ")+
  ylim(0,100)+
  theme_bw()+
  theme(panel.grid=element_blank(),
        legend.position = "right",
        axis.text.x  = element_text(size=14),
        axis.text.y  = element_text(size=14))
```


